Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-10-06 paper/paper_main.tex
updating affiliation for James

\usepackage{lineno}
\linenumbers

@@

\author{James W. Gardner}
\email{u6069809@anu.edu.au}
\affiliation{%
College of Science, Australian National University, Acton, ACT, 2601, Australia 
}%
\affiliation{%
 School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}

>>>>

%for line number
%\usepackage{lineno}
%\linenumbers

@@

\author{James W. Gardner}
\email{u6069809@anu.edu.au}
\affiliation{%
 ANU Centre for Gravitational Astrophysics, The Australian National University, Acton, ACT, 2601.
 %College of Science, Australian National University, Acton, ACT, 2601, Australia 
}%
\affiliation{%
 OzGrav-ANU, Australian Research Council Centre of Excellence for Gravitational-wave Discovery, The Australian National University, Acton, ACT, 2601.
}
\affiliation{%
 School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
